### 2015-05-15 whoop.tex
Addressed comment from Akis about false alarm rate.

We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option, but without this assumption the false alarm rate of \whoop is very high. In our experience so far, we have not missed any races by assuming non-overlapping parameters.  We also rely on the soundness of our best-effort environmental model, and on exploiting domain-specific knowledge related to entry point serialization by the Linux kernel.

>>>>

We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option.  Without this assumption we have observed \whoop reporting false alarms, and in our experience so far we have not missed any races by assuming non-overlapping parameters.  We also rely on the soundness of our best-effort environmental model, and on exploiting domain-specific knowledge related to entry point serialization by the Linux kernel.
